%-------------------------------------------------------------------------------
% work experience
%-------------------------------------------------------------------------------
\begin{section}[Experience]

  \entry%
  {Assistant Professor of Marketing} % Job Title
  {Tilburg University} % Organization
  {Tilburg, NL} % Location
  {2021 - to date} % Date
  {% Additional Information
    \begin{entrylist}
      \item Use deep learning models for text and video data in conjunction with econometric methods to reveal systematic bias in political messages across English and Spanish TV ads. 
      \item Implement machine learning models to predict long range forecasts of box office revenue of movies 
      \item Communicate the results of analyses and modeling through data visualization, presentations and writing.
      % \item Teach lectures and seminars in fields of Digital Marketing and Social Media Analytics. 
    %   \item Increase student engagement and learning by employing cooperative instructional strategies.
      \item Supervise approx. 10 independent researchers per year conducting Master's thesis research.
    \end{entrylist}
  }%


  \entry%
  {Postdoctoral Fellow in Marketing Research} % Job Title
  {University of Chicago Booth School of Business} % Organization
  {Chicago, US} % Location
  {2019 - 2021} % Date
  {% Additional Information
    \begin{entrylist}
      \item Estimate econometric models to uncover the causal effect of TV advertising on tweets about movies.
      \item Implement text analysis on large datasets ($\approx$ 6 million tweets) for stance detection and author profiling to estimate network effects of online political dissent.
      \item Communicate research findings at international scientific meetings and in writing.
    \end{entrylist}
  }%
  
    \entry%
  {Quantitative Researcher in Economics} % Job Title
  {University of Zurich} % Organization
  {Zurich, CH} % Location
  {2013 - 2019} % Date
  {% Additional Information
    \begin{entrylist}
      \item Estimate demand response to volume and sentiment of tweets in the movie industry. 
      \item Worked with large, unstructured text data ($\approx$ 300 million tweets) to compute sentiment indices and track social media conversation in the movie industry.
      %\item Perform econometric analysis estimate the effect of changing regulations on the number of minutes of advertising on UK public service broadcasters (eg. regression, fixed effects, instrumental variables).
      %\item Estimate structural consumer decision making models to understand gender differences in decision making under risk. 
      \item Main developer and co-instructor for \href{https://pp4rs.github.io/}{\faIcon{link} Programming Practices for Economists} and work as a maintainer and instructor for \href{https://uzhcrs.github.io/2019-02-07-zurich/}{\faIcon{link} Software Carpentry}.
      \item Coauthor a \href{https://lachlandeer.github.io/teaching/swc-dc/}{\faIcon{link} web tutorial} on reproducible research workflow management targeted at economists and business researchers.
      \item Communicate research findings at international scientific meetings and in writing.

    \end{entrylist}
  }%
  
\end{section}

